---
title: "Lab 00 - Hello IDS!"
author: "Julian Lee"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Peter Rabbit", "Julian", "Matthew", 
           "Matt"),
  github_username = c("mcgregors-garden", "Julianlee007", "mthw2304", 
                      "mw-mw-mw5051"), 
  colour = c("powderblue", "aquamarine", "#6B4BED", 
             "darkgreen"),
  hobby = c("Hopping", "football", "boardgames", 
            "movies"),
  favourite_number = c(2, 2, 3.141592653589793238462643383279502884197169, 5)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


Bar graph of the team's numbers and colors labelled by the member's usernames

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "GitHub Usernames", 
          y = "Favourite Numbers",
          title = "Diagram")
```

The command labs() is to determine the labels of the graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

If the data frame included everyone who took this course and not many people have the same hobbies, there would be too many different hobbies which would make the bar chart cluttered. As there would be many short bars, the data would be difficult to read or view. Therefore, using a piechart may be better in displaying the hobbies.  
